The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
Update manuscript.Rmd and manuscript.md
move

references: ../references/franks.bib
---

@@

Animal movement undoubtedly affects an individual's social environment (Strandburg-Peshkin et al. 2015). Movement is a dynamic process that is related to the resources an individual consumes within their home range and their general space use (Van Moorter et al. 2016). Collective movement can reduce group-level predation via detection-dilution trade-offs and improve information transfer about the quality or location of resources to other group members (Jolles et al. 2019). Social processes, movement decisions, and space use are therefore inextricably linked and multilayer networks represent a potential analytical framework for linking these processes (e.g. Mourier et al. 2019).

@@

In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals. Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make collective movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A collective movement layer could constitute similarity in movement for dyads (Long et al. 2014) or groups (Bode et al. 2011). This movement layer could be made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale (global migration: Flack et al. 2018). Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including traveling, interacting, or foraging (e.g. Muller et al. 2018; Finn et al. 2019) and construct a multilayer network based on behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019). Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al. 2018).

>>>>

references: ../references/refs.bib
---

@@

Animal movement undoubtedly affects an individual's social environment (Strandburg-Peshkin et al. 2015). Movement is a dynamic process that is related to the resources an individual consumes within their home range and the space that they use (Van Moorter et al. 2016). Collective movement can reduce group-level predation via detection-dilution trade-offs and improve information transfer about the quality or location of resources to other group members (Jolles et al. 2019). Social processes, movement decisions, and space use are inextricably linked and multilayer networks represent a potential analytical framework for linking these processes (e.g. Mourier et al. 2019).

@@

In contrast to spatial networks, where nodes represent spatial locations that are fixed in space, movement networks represent continuous and simultaneous movement trajectories of animals. Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make collective movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A collective movement layer could constitute similarity in movement for dyads (Long et al. 2014) or groups (Bode et al. 2011). This movement layer could be made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale (global migration: Flack et al. 2018). Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including traveling, interacting, or foraging (e.g. Muller et al. 2018; Finn et al. 2019) and construct a multilayer network based on behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019). Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al. 2018).
